---
title: "Week 4 Sum"
author: "Conner Langnas"
title-block-banner: true
title-block-style: default
toc: true
format: html
# format: pdf
---

---

## Tuesday, Jan 31

::: {.callout-important}
## TIL

Today we learned about 

1. Regression and linear regression
  * Motivation
  * 1_2 estimator
  * Inference
  * Prediction
2. Intro to statisical learning 
3. Multiple regression


```{R results = 'hide'}
#| output: false
library(ISLR2)
library(dplyr)
library(cowplot)
library(kableExtra)
library(htmlwidgets)
library(tidyverse)
```


## Statiscal Learning Diffrent types

* Supervised learning
  * Regression
  * Classification
* Unsupervised Learning
* Semi-Supervised Learning
* Renforcement learning











looking at scatter plots
using this data set 
https://online.stat.psu.edu/stat462/sites/onlinecourses.science.psu.edu.stat462/files/data/poverty/index.txt

```{r}
url <- "https://online.stat.psu.edu/stat462/sites/onlinecourses.science.psu.edu.stat462/files/data/poverty/index.txt"
df <- read_tsv(url)
df %>% head(., 20) %>% kable
```



```{r}
plt <- function(){
  plot(
  x,
  y,
  pch=20,
  xlab = "Pov %"
  ylab = "Birth rate (15-17)"
)
}
plt()


```
#```{r}
#1 echo if true
b0<- c(-2,0,2)
b1 <- c(0,1,2)


par(mfrow=c(3, 3))

for(B0 in b0){
  for(B1 in b1){
    plt()
    curve( B0 + B1 * x, 0, 30, add=T, col="red")
    title(main = paste("b0 = "
```
goal is get a straight line that fits most of the data






## Thursday, Feb 2



::: {.callout-important}
## TIL

Include a _very brief_ summary of what you learnt in this class here. 

Today, I learnt the following concepts in class:

1. Item 1 change
1. Item 2
1. Item 3
:::

Provide more concrete details here, e.g., 

In class we learnt how to use the `map` function to create multiple regression diagnostic plots

#```{R results='hide', fig.height=4}
par(mfcol=c(2, 3), mar=c(3.5, 3.5, 2, 1), mgp=c(2.4, 0.8, 0))
mtcars %>%
  split(.$cyl) %>%
  map(~ lm(mpg ~ wt, data = .x)) %>%
  map(function(x)plot(x, which=c(1, 2)))
```


[^footnote]: You can include some footnotes here